\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-15 paper/main.tex
Updated citation and author
Fixed a type

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato et al.}

@@

\textbf{Handling bugs from nighly builds requires saving wheels.}
Many of the reproducible bugs rely on the libraries' nightly builds,
which are available for a limited amount of time. To ensure that bugs
reported on these builds remain reproducible, it is necessary to save
Python wheel files (.whl)~\cite{wheels} for the correspondind builds.

>>>>

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Naziri et al.}

@@

\textbf{Handling bugs from nightly builds requires saving wheels.}
Many of the reproducible bugs rely on the libraries' nightly builds,
which are available for a limited amount of time. To ensure that bugs
reported on these builds remain reproducible, it is necessary to save
Python wheel files (.whl)~\cite{wheels} for the correspondind builds.
